\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{ifthen}
\usepackage{lastpage}
\usepackage{pgffor}
\usepackage{setspace}

% Define the fancy headers and footers.
\pagestyle{fancyplain}
\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/cmara/meeting-note-sheets}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

% Define Notes Lines
\newcommand{\notelines }[3][\empty]{%
    \noindent\vspace{10pt}\\
    \foreach \n in {1,...,#2}{%
        \ifthenelse{\equal{#1}{\empty}}
            {\rule{#3}{0.5pt}\\}
            {\rule{#3}{0.5pt}\vspace{#1}\\}
        }
}

\begin{document}

\begin{center}
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Business Meeting Note Sheet, Not official submission.}
\end{center}

\section{Meeting Called to Order}
When was the meeting called to order (date \& time) and by whom?
\notelines[12pt]{1}{\textwidth}

\section{Attendance}
Put out attendance sheet and ask everyone to sign in.

\section{Reports}

\subsection{Secretary's Report}
Was the secretary's report voted in? Under what conditions (as published, as read)? How was it approved (by voice vote)?
\notelines[12pt]{1}{\textwidth}

\subsection{Treasurer's Report}
Was the treasurer's report voted in? Under what conditions (as published, as read)? How was it approved (by voice vote)?
\notelines[12pt]{1}{\textwidth}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
\notelines[12pt]{5}{\textwidth}

\subsubsection{Repeater Trustees Report}
\notelines[12pt]{5}{\textwidth}

\subsubsection{Field Day Committee Report}
\notelines[12pt]{5}{\textwidth}

\section{Old Business}
\notelines[12pt]{5}{\textwidth}

\newpage

\section{New Business}

\subsection{New CMARA Members}
\notelines[12pt]{5}{\textwidth}

\subsection{Other New Business}
\notelines[12pt]{5}{\textwidth}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
\notelines[12pt]{5}{\textwidth}

\newpage

\subsection{Other News}
\notelines[12pt]{5}{\textwidth}

\section{Next Meeting}
\notelines[12pt]{3}{\textwidth}

\section{Meeting Adjourned}
When was the meeting closed (date \& time) and by whom?

\notelines[12pt]{1}{\textwidth}

\section{Post-Meeting Presentation}
\notelines[12pt]{5}{\textwidth}

\end{document}
