\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-note-sheets}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Meeting Format Reminder}
\end{center}

\begin{enumerate}

  \item \textbf{Meeting called to order}
  \begin{enumerate}
    \item Formally call the meeting to order.
  \end{enumerate}

  \item \textbf{Attendance}
  \begin{enumerate}
    \item Remind folks to sign in using the attendance sheet in the front.
    \item It's club routine to go around the room and have everyone say their name and callsign.
  \end{enumerate}

  \item \textbf{Reports}
  \begin{enumerate}
    \item Secretary's Report - There must be a motion to accept.
    \item Treasurer's Report - There must be a motion to accept.
    \item Committee Reports
    \begin{enumerate}
      \item Membership Committee Report
      \item Repeater Trustees Report
      \item Field Day Committee Report
    \end{enumerate}
  \end{enumerate}

  \item \textbf{Old Business}
  \begin{enumerate}
    \item Ask for any old business. This must be dealt with first.
  \end{enumerate}

  \item \textbf{New Business}
  \begin{enumerate}
    \item Ask the treasurer or secretary if there are any new member applications that need voting. Vote if needed.
    \item Ask for any other new business. This is for CMARA related business, keep in mind there is a section for ``For the Good of the Club''.
  \end{enumerate}

  \item \textbf{For the Good of the Club}
  \begin{enumerate}
    \item New Hams \& Upgrades: Ask if anyone has a new license (either new ham or upgrade).
    \item Ask for any other news. This is a great time for community announcements, or anything else that isn't CMARA business specific.
  \end{enumerate}

  \item \textbf{Next Meeting}
  \begin{enumerate}
    \item Declare when the next meeting is.
    \item If there are to be any other gatherings in the meantime (such as planned board meetings) mention those here.
  \end{enumerate}

  \item \textbf{Meeting Adjourned}
  \begin{enumerate}
    \item Formally close the meeting.
  \end{enumerate}

  \item \textbf{Presentation}
  \begin{enumerate}
    \item Introduce the presenter and what they're presenting.
  \end{enumerate}

\end{enumerate}

\end{document}
